---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MemorablePackageName

<!-- badges: start -->
<!-- badges: end -->

The goal of MemorablePackageName is to ...

## Installation

You can install the development version of MemorablePackageName like so:

``` r
install.packages("MemorablePackageName")
```

## Example

This is a basic example which shows you how to solve a common problem, such as multiplying two numbers:

```{r example}
library(MemorablePackageName)
print(multiplier(3, 5))
```

This package also contains a raw dataset that can be used in case you happen to need some cool information. The dataset in this package includes data about the metabolites of patients with delirium. Wow!

Here's a summary of the data:
```{r}
Metabolomics_data <- read_excel("data-raw/testPCA.xlsx")
summary(Metabolomics_data)
```
